### 2015-07-01 narrative/data-desc.tex
edits on description of data.

\paragraph{Proposed research approach:} 
We will design and deveop new APIs through which users can describe the utility of data
based on their expectations.

>>>>

\paragraph{Proposed research approach:} 
We will design and deveop new APIs through which users can describe the utility of data
based on their expectations. This can be done by plugging user level functions that will
partition user level data into objects and be executed by the middleware to calculate the 
utility value for each object. The utility value along with other metadata will be encapsulated
by the middleware and utilized by the underlying storage system to management data placement.
